The abundance of Bullet-Groups in $\Lambda$CDM

### 2014-03-20 paper/ms.tex
goes for a second round of comments

Neverthless, comparing the number for group and cluster samples in the
last row of Table \ref{table:numbers} we can already predict that a
fixed redshift the number density of bullets similar to \bullg that
three times larger for groups than for clusters.

>>>>

Neverthless, comparing the number for group and cluster samples in the
last row of Table \ref{table:numbers} we can already predict that a
fixed redshift the number density of halos in the groups sample similar to \bullg is
$\sim 6.0\times 10^{-7}$ Mpc$^{-3}$, three times larger than the
estimate for halos in the group sample.
